DATA 624 Homework 8

### 2020-04-09 DATA624/HW8.Rmd
More work on HW 8

```{r}
nnet_grid <- expand.grid(.decay = c(0, 0.01, .1), .size = c(1:10), .bag = FALSE)
nnet_maxnwts <- 5 * (ncol(trainingData$x) + 1) + 5 + 1
nnet_model <- train(x = trainingData$x,
                    y = trainingData$y,
                    method = "avNNet",
                    preProcess = c("center", "scale"),
                    tuneGrid = nnet_grid,
                    trControl = trainControl(method = "cv"),
                    linout = TRUE,
                    trace = FALSE,
                    MaxNWts = nnet_maxnwts,
                    maxit = 500)
nnet_model
```

@@

pls_model <- train(
  y ~ ., data = train_df, method = "pls",
  center = TRUE,
  trControl = trainControl("cv", number = 10),
  tuneLength = 25
)
```

@@

>>>>

```{r neural_network_model}
nnet_grid <- expand.grid(.decay = c(0, 0.01, .1), .size = c(1:10), .bag = FALSE)
nnet_maxnwts <- 5 * (ncol(trainingData$x) + 1) + 5 + 1
nnet_model <- train(x = trainingData$x,
                    y = trainingData$y,
                    method = "avNNet",
                    preProcess = c("center", "scale"),
                    tuneGrid = nnet_grid,
                    trControl = trainControl(method = "cv"),
                    linout = TRUE,
                    trace = FALSE,
                    MaxNWts = nnet_maxnwts,
                    maxit = 500)
nnet_model
```

@@

pls_model <- train(
  y ~ ., data = train_df, method = "pls",
  center = TRUE,
  trControl = trainControl("cv", number = 10),
  tuneLength = 25
)

pls_predictions <- predict(pls_model, test_df)

results <- data.frame(t(postResample(pred = pls_predictions, obs = test_df$y))) %>%
  mutate("Model"= "PLS")
```

@@

#### KNN Model

```{r}
knn_model <- train(y ~ ., data = train_df, method = "knn",
                   preProcess = c("center"), 
                   trControl = trainControl("cv", number = 10),
                   tuneLength = 25)
knn_model

knn_predictions <- predict(knn_model, test_df)

results <- data.frame(t(postResample(pred = knn_predictions, obs = test_df$y))) %>%
  mutate("Model"= "KNN") %>% rbind(results)
```

#### MARS Model

```{r}
MARS_grid <- expand.grid(.degree = 1:2, .nprune = 2:15)
MARS_model <- train(y ~ ., data = train_df, method = "earth",
                    tuneGrid = MARS_grid,
                    preProcess = c("center"),
                    tuneLength = 25)
MARS_model

MARS_predictions <- predict(MARS_model, test_df)

results <- data.frame(t(postResample(pred = MARS_predictions, obs = test_df$y))) %>%
  mutate("Model"= "MARS") %>% rbind(results)
```

#### SVM Model

```{r}
SVM_model <- train(y ~ ., data = train_df, method = "svmRadial",
                   preProcess = c("center"),
                   tuneLength = 25,
                   trControl = trainControl(method = "cv"))
SVM_model

SVM_predictions <- predict(SVM_model, test_df)

results <- data.frame(t(postResample(pred = SVM_predictions, obs = test_df$y))) %>%
  mutate("Model"= "SVM") %>% rbind(results)
```

#### Neural Network Model

```{r}
nnet_grid <- expand.grid(.decay = c(0, 0.01, .1), .size = c(1:10), .bag = FALSE)
nnet_maxnwts <- 5 * ncol(train_df) + 5 + 1
nnet_model <- train(y ~ ., data = train_df, method = "avNNet",
                    preProcess = c("center"),
                    tuneGrid = nnet_grid,
                    trControl = trainControl(method = "cv"),
                    linout = TRUE,
                    trace = FALSE,
                    MaxNWts = nnet_maxnwts,
                    maxit = 500)
nnet_model

nnet_predictions <- predict(nnet_model, test_df)

results <- data.frame(t(postResample(pred = nnet_predictions, obs = test_df$y))) %>%
  mutate("Model"= "Neural Network") %>% rbind(results)
```

#### Summary

```{r}
results %>%
  select(Model, RMSE, Rsquared, MAE) %>%
  arrange(RMSE) %>%
  kable() %>%
  kable_styling()
```
